---
title: "Lab 1"
author: "Jackson Janes"
date: "Due on 02/03 at 11:59 pm"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r upload}
library(tidyverse)
library(broom)
library(Lahman)
library(retrosheet)
library(ggplot2)
```

**Instructions:** This lab report needs to be professional. Only report relevant and finalized code. Your writing should be concise and void of spelling errors. Use code chunk options to hide unnecessary messages/warnings. Your report should be reproducible. Reports that involve simulations need to have the random seed specified so that simulation results are reproducible. You are allowed to work on this lab assignment in groups of 2-3. You still need to submit an individual lab report if you do work in a group, and you need to list your collaborators. \vspace*{0.5cm}

**Question 1** In lecture it was demonstrated that baseball is a game of offense, pitching, and defense with a regression model that considered expected run differential as a function of explanatory variables OPS, WHIP, and FP. Do the following:

-   Fit a similar regression model with runs as the response variable. Report problems with this model. Investigate problematic residuals to discover what went wrong. Fix the problem with this model by adding categorical variable(s) to the list of explanatory variables. Briefly explain what went wrong.

```{r question1a}

#OPS calculation
#OBP = (H + BB + HBP) / (AB + BB + HBP + SF)
#SLG = ((X1B + 2*X2B + 3*X3B + 4*HR) / AB)

#OPS = OBP + SLG

#WHIP calculation
#WHIP = 3* (HA + BBA/IPouts)

#FP calculation

dat <- Teams %>%
  dplyr::select(yearID, franchID, W, L, AB, H, X2B, X3B, HR, BB, HBP, SF, HA, HRA, BBA, SOA, IPouts, FP, R, RA) %>%
  filter(yearID >= 1900) %>%
  replace_na(list(HBP = 0, SF = 0)) %>%
  mutate(X1B = H - (X2B - X3B - HR)) %>%
  mutate(RD = (R - RA) / (W + L), X1B = H - (X2B + X3B + HR)) %>%
  mutate(OBP = (H + BB + HBP) / (AB + BB + HBP + SF)) %>%
  mutate(SLG = (X1B + 2*X2B + 3*X3B + HR) / AB) %>%
  mutate(OPS = OBP + SLG) %>%
  mutate(WHIP = 3*(HA + BBA) / IPouts)
  
question1 <- lm(R ~ OPS + WHIP + FP, data = dat)

summary(question1)
pairs(dat %>% select(RD, OPS, WHIP, FP))
par(mfrow = c(2,2))
plot(question1)

dat_aug <- augment(question1, data = dat)
dat_aug %>%
  mutate(rmse = sqrt((mean(.resid^2)))) %>%
  summarize(N = n(),
            within_1rmse = sum(abs(.resid) < rmse),
            within_2rmse = sum(abs(.resid) < 2 * rmse)) %>%
  mutate(within_1rmse_pct = within_1rmse / N,
         within_2rmse_pct = within_2rmse / N)

m_glm <- glm(RD ~ OPS + WHIP + FP, data = dat)
pchisq(m_glm$deviance, m_glm$df.residual, lower = FALSE)

dat_aug %>% filter(abs(.resid) >= 1) %>%
  select(yearID, franchID, R, OPS, WHIP, FP, .resid, .fitted) %>%
  mutate(across(3:8, round, 3)) %>%
  arrange(desc(.resid))

dat_aug %>% filter(.fitted >= 2) %>%
  select(yearID, franchID, R, OPS, WHIP, FP, .resid, .fitted)

qqnorm(resid(question1)); qqline(resid(question1))
abline(a=0.5, b=0, lty =2, col = "blue")

plot(table(dat_aug %>% filter(abs(.resid) >= 0.5) %>%
             pull(yearID)), ylab = "number of model under counts")
```

-   We can significantly improve the regression model in the notes through a principled rescaling of OPS, WHIP, and FP. Split the Teams data frame by {yearID} and, for each year, create variables {OPSscale = OPS/avgOPS}, {WHIPscale = avgWHIP/WHIP}, and {FPscale = avgFP/FP} which require you to first create league average variables {avgOPS}, {avgWHIP}, and {avgFP}. Fit the linear regression model with runs differential as the response and explanatory variables {OPSscale}, {WHIPscale}, and {FPscale}, and report relevant output. Why does this model perform so much better than the model in the notes? Support your answer. Hint: functions {split}, {do.call}, and {lapply} are useful.

```{r question1b, include=FALSE}
TeamsbyYr <- split(dat, f = dat$yearID)

newmodel <- do.call(rbind, lapply(TeamsbyYr, function(fxn_newvar) {avgWHIP <- 3*(sum(fxn_newvar$BBA) + sum(fxn_newvar$HA))/sum(fxn_newvar$IP)
avgOBP <-(sum(fxn_newvar$H + fxn_newvar$BB + fxn_newvar$HBP)) / sum(fxn_newvar$AB + fxn_newvar$BB, fxn_newvar$HBP + fxn_newvar$SF)
avgSLG <- sum(fxn_newvar$X1B + 2*fxn_newvar$X2B + 3*fxn_newvar$X3B + 4*fxn_newvar$HR) / sum(fxn_newvar$AB)
avgOPS <- avgOBP + avgSLG
fxn_newvar <- fxn_newvar %>% mutate(WHIPscale = avgWHIP / WHIP) %>%
  mutate(OPSscale = OPS/ avgOPS) %>%
  mutate(FPscale = mean(fxn_newvar$FP) / fxn_newvar$FP)}))
```

```{r q1banswer}
q1b <- lm(RD ~ OPSscale + WHIPscale + FPscale, data = newmodel)

summary(q1b)
```
This model performs much better because it focuses on each season as a whole, which makes the outliers less impactful to the model.

**Question 2** Choose 3 batters and 3 pitchers that have played in at least 10 seasons and do the following:

-   Display the seasonal statistics for these players. The following statistics should be included for batters (derivations of unconventional statistics are in parentheses): year, G, AB, R, H, X2B, X3B, HR, RBI, SB, CS, SBpct (SB / (SB + CS)), BB, SO, OBP, SLG, OPS. The following statistics should be included for pitchers: year, W, L, IPouts, H, ER, HR, BB, HBP, SO, ERA, WHIP, SOper9 (SO / IP \* 9), SOperBB (SO / BB). These statistics can be found in or computed from statistics that are found in the \texttt{Batting} and \texttt{Pitching} dataframes in the \texttt{Lahman} package.

Alfonso Soriano

```{r soriano, include=FALSE}
# Alfonso Soriano career stats

soriano <- Batting %>%
  select(playerID, yearID, G, AB, R, H, X2B, X3B, HR, RBI, SB, CS, BB, SO, HBP, SF) %>%
  filter(playerID == "soriaal01") %>%
  mutate(X1B = H - (X2B + X3B + HR)) %>%
  mutate(OBP = (H + BB + HBP) / (AB + BB + HBP + SF)) %>%
  mutate(SLG = (X1B + 2*X2B + 3*X3B + 4*HR) / AB) %>%
  mutate(OPS = OBP + SLG) %>%
  mutate(SBpct = SB / (SB + CS))

soriano2 <- soriano %>%
  mutate(CarG = sum(soriano$G)) %>% 
  mutate(CarAB = sum(soriano$AB)) %>%
  mutate(CarR = sum(soriano$R)) %>%
  mutate(CarH = sum(soriano$H)) %>%
  mutate(CarX1B = sum(soriano$X1B)) %>%
  mutate(CarX2B = sum(soriano$X2B)) %>%
  mutate(CarX3B = sum(soriano$X3B)) %>%
  mutate(CarHR = sum(soriano$HR)) %>%
  mutate(CarRBI = sum(soriano$RBI)) %>%
  mutate(CarSB = sum(soriano$SB)) %>%
  mutate(CarCS = sum(soriano$CS)) %>%
  mutate(CarSBpct = CarSB / (CarSB + CarCS)) %>%
  mutate(CarBB = sum(soriano$BB)) %>%
  mutate(CarSO = sum(soriano$SO)) %>%
  mutate(CarHBP = sum(soriano$HBP)) %>%
  mutate(CarSF = sum(soriano$SF)) %>%
  mutate(CarOBP = (CarH +CarBB + CarHBP) / (CarAB + CarBB + CarHBP + CarSF)) %>%
  mutate(CarSLG = (CarX1B + 2*CarX2B + 3*CarX3B + 4*CarHR) / CarAB) %>%
  mutate(CarOPS = CarOBP + CarSLG) %>%
  mutate(CarYrs = n_distinct(yearID)) %>%
  mutate(Name = "Alfonso Soriano")

soriano_career <- soriano2 %>%
  select(Name, CarYrs, CarG, CarAB, CarR, CarH, CarX2B, CarX3B, CarHR, CarRBI, CarSB, CarCS, CarSBpct, CarBB, CarSO, CarOBP, CarSLG, CarOPS)
also <- head(soriano_career, 1)
  
```

Dexter Fowler
```{r fowler, include=FALSE}
# Dexter Fowler career stats

fowler <- Batting %>%
  select(playerID, yearID, G, AB, R, H, X2B, X3B, HR, RBI, SB, CS, BB, SO, HBP, SF) %>%
  filter(playerID == "fowlede01") %>%
   mutate(X1B = H - (X2B + X3B + HR)) %>%
  mutate(OBP = (H + BB + HBP) / (AB + BB + HBP + SF)) %>%
  mutate(SLG = (X1B + 2*X2B + 3*X3B + 4*HR) / AB) %>%
  mutate(OPS = OBP + SLG) %>%
  mutate(SBpct = SB / (SB + CS))

fowler2 <- fowler %>%
  mutate(CarG = sum(fowler$G)) %>% 
  mutate(CarAB = sum(fowler$AB)) %>%
  mutate(CarR = sum(fowler$R)) %>%
  mutate(CarH = sum(fowler$H)) %>%
  mutate(CarX1B = sum(fowler$X1B)) %>%
  mutate(CarX2B = sum(fowler$X2B)) %>%
  mutate(CarX3B = sum(fowler$X3B)) %>%
  mutate(CarHR = sum(fowler$HR)) %>%
  mutate(CarRBI = sum(fowler$RBI)) %>%
  mutate(CarSB = sum(fowler$SB)) %>%
  mutate(CarCS = sum(fowler$CS)) %>%
  mutate(CarSBpct = CarSB / (CarSB + CarCS)) %>%
  mutate(CarBB = sum(fowler$BB)) %>%
  mutate(CarSO = sum(fowler$SO)) %>%
  mutate(CarHBP = sum(fowler$HBP)) %>%
  mutate(CarSF = sum(fowler$SF)) %>%
  mutate(CarOBP = (CarH + CarBB + CarHBP) / (CarAB + CarBB + CarHBP + CarSF)) %>%
  mutate(CarSLG = (CarX1B + 2*CarX2B + 3*CarX3B + 4*CarHR) / CarAB) %>%
  mutate(CarOPS = CarOBP + CarSLG) %>%
  mutate(CarYrs = n_distinct(yearID)) %>%
  mutate(Name = "Dexter Fowler")

fowler_career <- fowler2 %>%
  select(Name, CarYrs, CarG, CarAB, CarR, CarH, CarX2B, CarX3B, CarHR, CarRBI, CarSB, CarCS, CarSBpct, CarBB, CarSO, CarOBP, CarSLG, CarOPS)
defo <- head(fowler_career, 1)
```

Jason Heyward
```{r heyward, include=FALSE}
# Jason Heyward career stats

heyward <- Batting %>%
  select(playerID, yearID, G, AB, R, H, X2B, X3B, HR, RBI, SB, CS, BB, SO, HBP, SF) %>%
  filter(playerID == "heywaja01") %>%
     mutate(X1B = H - (X2B + X3B + HR)) %>%
  mutate(OBP = (H + BB + HBP) / (AB + BB + HBP + SF)) %>%
  mutate(SLG = (X1B + 2*X2B + 3*X3B + 4*HR) / AB) %>%
  mutate(OPS = OBP + SLG)

heyward2 <- heyward %>%
  mutate(CarG = sum(heyward$G)) %>% 
  mutate(CarAB = sum(heyward$AB)) %>%
  mutate(CarR = sum(heyward$R)) %>%
  mutate(CarH = sum(heyward$H)) %>%
  mutate(CarX1B = sum(heyward$X1B)) %>%
  mutate(CarX2B = sum(heyward$X2B)) %>%
  mutate(CarX3B = sum(heyward$X3B)) %>%
  mutate(CarHR = sum(heyward$HR)) %>%
  mutate(CarRBI = sum(heyward$RBI)) %>%
  mutate(CarSB = sum(heyward$SB)) %>%
  mutate(CarCS = sum(heyward$CS)) %>%
  mutate(CarSBpct = CarSB / (CarSB + CarCS)) %>%
  mutate(CarBB = sum(heyward$BB)) %>%
  mutate(CarSO = sum(heyward$SO)) %>%
  mutate(CarHBP = sum(heyward$HBP)) %>%
  mutate(CarSF = sum(heyward$SF)) %>%
  mutate(CarOBP = (CarH + CarBB + CarHBP) / (CarAB + CarBB + CarHBP + CarSF)) %>%
  mutate(CarSLG = (CarX1B + 2*CarX2B + 3*CarX3B + 4*CarHR) / CarAB) %>%
  mutate(CarOPS = CarOBP + CarSLG) %>%
  mutate(CarYrs = n_distinct(yearID)) %>%
  mutate(Name = "Jason Heyward")

heyward_career <- heyward2 %>%
  select(Name, CarYrs, CarG, CarAB, CarR, CarH, CarX2B, CarX3B, CarHR, CarRBI, CarSB, CarCS, CarSBpct, CarBB, CarSO, CarOBP, CarSLG, CarOPS)
jahe <- head(heyward_career, 1)
```

Kerry Wood
```{r wood, include=FALSE}
# Kerry Wood career stats

wood <- Pitching %>%
  select(playerID, yearID, W, L, IPouts, H, ER, HR, BB, HBP, SO, ERA) %>%
  filter(playerID == "woodke02") %>%
  mutate(IP = IPouts / 3) %>%
  mutate(WHIP = 3*(H + BB) / IPouts) %>%
  mutate(SOper9 = (SO/IP) * 9) %>%
  mutate(SOperBB = SO / BB)

wood2 <- wood %>%
  mutate(CarYrs = n_distinct(wood$yearID)) %>%
  mutate(CarW = sum(wood$W)) %>% 
  mutate(CarL = sum(wood$L)) %>%
  mutate(CarIPouts = sum(wood$IPouts)) %>%
  mutate(CarH = sum(wood$H)) %>%
  mutate(CarER = sum(wood$ER)) %>%
  mutate(CarHR = sum(wood$HR)) %>%
  mutate(CarBB = sum(wood$BB)) %>%
  mutate(CarHBP = sum(wood$HBP)) %>% 
  mutate(CarSO = sum(wood$SO)) %>%
  mutate(CarIP = sum(wood$IP)) %>%
  mutate(CarERA = 9*(CarER / CarIP)) %>%
  mutate(CarWHIP = 3*(CarH + CarBB) / CarIPouts) %>%
  mutate(CarSOper9 = (CarSO / CarIP) * 9) %>%
  mutate(CarSOperBB = CarSO/ CarBB) %>%
  mutate(CarYrs = n_distinct(yearID)) %>%
  mutate(Name = "Kerry Wood")

wood_career <- wood2 %>%
  select(Name, CarYrs, CarW, CarL, CarIPouts, CarH, CarER, CarHR, CarBB, CarHBP, CarSO, CarERA, CarWHIP, CarBB, CarSOper9, CarSOperBB)
kewo <- head(wood_career, 1)
```

Carlos Zambrano
```{r zambrano, include=FALSE}
# Carlos Zambrano career stats

zambrano <- Pitching %>%
  select(playerID, yearID, W, L, IPouts, H, ER, HR, BB, HBP, SO, ERA) %>%
  filter(playerID == "zambrca01") %>%
  mutate(IP = IPouts / 3) %>%
  mutate(WHIP = 3*(H + BB) / IPouts) %>%
  mutate(SOper9 = (SO/IP) * 9) %>%
  mutate(SOperBB = SO / BB)

zambrano2 <- zambrano %>%
  mutate(CarYrs = n_distinct(zambrano$yearID)) %>%
  mutate(CarW = sum(zambrano$W)) %>% 
  mutate(CarL = sum(zambrano$L)) %>%
  mutate(CarIPouts = sum(zambrano$IPouts)) %>%
  mutate(CarH = sum(zambrano$H)) %>%
  mutate(CarER = sum(zambrano$ER)) %>%
  mutate(CarHR = sum(zambrano$HR)) %>%
  mutate(CarBB = sum(zambrano$BB)) %>%
  mutate(CarHBP = sum(zambrano$HBP)) %>% 
  mutate(CarSO = sum(zambrano$SO)) %>%
  mutate(CarIP = sum(zambrano$IP)) %>%
  mutate(CarERA = 9*(CarER / CarIP)) %>%
  mutate(CarWHIP = 3*(CarH + CarBB) / CarIPouts) %>%
  mutate(CarSOper9 = (CarSO / CarIP) * 9) %>%
  mutate(CarSOperBB = CarSO/ CarBB) %>%
  mutate(CarYrs = n_distinct(yearID)) %>%
  mutate(Name = "Carlos Zambrano")

zambrano_career <- zambrano2 %>%
  select(Name, CarYrs, CarW, CarL, CarIPouts, CarH, CarER, CarHR, CarBB, CarHBP, CarSO, CarERA, CarWHIP, CarBB, CarSOper9, CarSOperBB)
caza <- head(zambrano_career, 1)

```

Jeff Samardzija
```{r samardzija, include=FALSE}
# Jeff Samardzija career stats

samardzija <- Pitching %>%
  select(playerID, yearID, W, L, IPouts, H, ER, HR, BB, HBP, SO, ERA) %>%
  filter(playerID == "samarje01") %>%
  mutate(IP = IPouts / 3) %>%
  mutate(WHIP = 3*(H + BB) / IPouts) %>%
  mutate(SOper9 = (SO/IP) * 9) %>%
  mutate(SOperBB = SO / BB)

samardzija2 <- samardzija %>%
  mutate(CarYrs = n_distinct(samardzija$yearID)) %>%
  mutate(CarW = sum(samardzija$W)) %>% 
  mutate(CarL = sum(samardzija$L)) %>%
  mutate(CarIPouts = sum(samardzija$IPouts)) %>%
  mutate(CarH = sum(samardzija$H)) %>%
  mutate(CarER = sum(samardzija$ER)) %>%
  mutate(CarHR = sum(samardzija$HR)) %>%
  mutate(CarBB = sum(samardzija$BB)) %>%
  mutate(CarHBP = sum(samardzija$HBP)) %>% 
  mutate(CarSO = sum(samardzija$SO)) %>%
  mutate(CarIP = sum(samardzija$IP)) %>%
  mutate(CarERA = 9*(CarER / CarIP)) %>%
  mutate(CarWHIP = 3*(CarH + CarBB) / CarIPouts) %>%
  mutate(CarSOper9 = (CarSO / CarIP) * 9) %>%
  mutate(CarSOperBB = CarSO/ CarBB) %>%
  mutate(CarYrs = n_distinct(yearID)) %>%
  mutate(Name = "Jeff Samardzija")

samardzija_career <- samardzija2 %>%
  select(Name, CarYrs, CarW, CarL, CarIPouts, CarH, CarER, CarHR, CarBB, CarHBP, CarSO, CarERA, CarWHIP, CarBB, CarSOper9, CarSOperBB)
jesa <- head(samardzija_career, 1)
```

-   Create career stat lines for each of the players that you selected. Be careful about how these statistics are calculated.
```{r question2a}
# Combined career batting stats for Alfonso Soriano, Dexter Fowler, and Jason Heyward
Batter_Career <- bind_rows(also, defo, jahe); Batter_Career

# Combined career pitching stats for Kerry Wood, Carlos Zambrano, and Jeff Samardzija
Pitcher_Career <<- bind_rows(kewo, caza, jesa); Pitcher_Career

```


-   Provide a plot for career trajectories for one batting and one pitching statistic of your choice. These are two separate graphics, one for the batters and one for the pitchers. The graphics that you produce should display the trajectories of the 3 batters and the 3 pitchers. Provide interesting commentary on your graphic.

```{r question 2b}
#Batting Statistic: Hits

ggplot(data = soriano, mapping = aes(x = yearID, y = H)) + geom_point() + geom_smooth()

ggplot(data = fowler, mapping = aes(x = yearID, y = H)) + geom_point() + geom_smooth()

ggplot(data = heyward, mapping = aes(x = yearID, y = H)) + geom_point() + geom_smooth()

#Pitching Statistic: Wins

ggplot(data = wood, mapping = aes(x = yearID, y = W)) + geom_point() + geom_smooth()

ggplot(data = zambrano, mapping = aes(x = yearID, y = W)) + geom_point() + geom_smooth()

ggplot(data = samardzija, mapping = aes(x = yearID, y = W)) + geom_point() + geom_smooth()
```
All three hitters seemed to be in their "prime" in roughly the middle of their careers. There is a clear decline from this point on in their careers, and the dropoff in hits is pretty dramatic for all three players.

The plots of Carlos Zambrano and Jeff Samardzija are roughly what I would expect a career trajectory to look like: They struggled at first, built up a few really solid years in the middle of their careers, and then declined in their final years in the MLB. Kerry Wood's plot is rather interesting, as he had his best years very early and then experienced a fairly steep decline after that point. I did not expect that dropoff to be as dramatic as depicted above, but it is interesting how consistent and how little variation that was later in his career.

**Question 3** Problem 2 on page 28 of Analyzing Baseball Data with R

(a) Gibson started 34 games for the Cardinals in 1968. What fraction of these games were completed by Gibson?

```{r question3a}

q3a <- Pitching %>%
 select(playerID, yearID, teamID, G, CG) %>%
  filter(playerID == "gibsobo01") %>%
  filter(yearID == "1968") %>%
  mutate(CGpct = CG / G) %>%
  select(CGpct); q3a
```

(b) What was Gibson's ratio of strikeouts to walks this season?

```{r question3b}
q3b <- Pitching %>%
  select(playerID, yearID, SO, BB) %>%
  filter(playerID == "gibsobo01") %>%
  filter(yearID == "1968") %>%
  mutate(KBBratio = SO/ BB) %>%
  select(KBBratio); q3b
```

(c) One can compute Gibson's innings pitched by dividing IPouts by three. How many innings did Gibson pitch this season?

```{r question3c}
q3c <- Pitching %>%
  select(playerID, yearID, IPouts) %>%
  filter(playerID == "gibsobo01") %>%
  filter(yearID == "1968") %>%
  mutate(IP = IPouts / 3) %>%
  select(IP); q3c

```

(d) A modern measure of pitching effectiveness is WHIP, the average number of hits and walks allowed per inning. What was Gibson's WHIP for the 1968 season?

```{r question3d}
q3d <- Pitching %>%
  select(playerID, yearID, H, BB, IPouts) %>%
  filter(playerID == "gibsobo01") %>%
  filter(yearID == "1968") %>%
  mutate(WHIP = 3*(H + BB) / IPouts) %>%
  select(WHIP); q3d

```

**Question 4** Problem 3 on page 29 of Analyzing Baseball Data with R

(Retrosheet Game Log) Jim Bunning pitched a perfect game on Father's Day on June 21, 1964. Some details about this particular game can be found from the Retrosheet game logs.

(a) What was the time in hours and minutes of this particular game?

```{r question4a}
q4a <- getRetrosheet(type = "game", year = 1964) %>%
  select(Date, Duration, WinPNm) %>%
  filter(WinPNm == "Jim Bunning") %>%
  filter(Date == "19640621") %>%
  mutate(Hrs = Duration / 60) %>%
  mutate(Hours = as.integer(Hrs)) %>%
  mutate(Minutes = (Hrs - Hours) * 60) %>%
  select(Hours, Minutes); q4a

```

(b) Why is the attendance value in this record equal to zero?

```{r question4b}
q4b <- getRetrosheet(type = "game", year = 1964) %>%
  select(Date, Attendance, WinPNm) %>%
  filter(WinPNm == "Jim Bunning") %>%
  filter(Date == "19640621") %>%
  select(Attendance); q4b
```
The attendance value in this record is equal to zero because it was the first half of a doubleheader. Fans likely only needed one ticket to attend both games, so `0` was recorded for the first game, and the actual attendance was entered for the second game of the doubleheader.

(c) How many extra base hits did the Phillies have in this game? (We know that the Mets had no extra base hits this game.)

```{r question4c}
q4c <- getRetrosheet(type = "game", year = 1964) %>%
  select(Date, WinPNm, VisD, VisT, VisHR, HmD, HmT, HmHR) %>%
  filter(WinPNm == "Jim Bunning") %>%
  filter(Date == "19640621") %>%
  mutate(TotXBH = VisD + VisT + VisHR) %>%
  select(TotXBH); q4c

```

(d) What was the Phillies' on-base percentage in this game?

```{r question4d}
q4d <- getRetrosheet(type = "game", year = 1964) %>%
     select(WinPNm, Date, VisH, VisBB, VisHBP, VisAB, VisSF) %>%
     filter(WinPNm == "Jim Bunning") %>%
     filter(Date == "19640621") %>%
     mutate(OBP = (VisH + VisBB + VisHBP) / (VisAB + VisBB + VisHBP + VisSF)) %>% 
     select(OBP); q4d

```
