---
title: "Lab 2"
author: ""
date: "Due on 02/17/23 at 11:59 pm"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(Lahman)
library(tidyverse)
library(retrosheet)
```

**Question 1** 

  - Construct a data frame which includes the following variables from the \texttt{Teams} data frame in the \texttt{Lahman} package: \texttt{yearID}, \texttt{teamID}, \texttt{AB}, \texttt{SO}, \texttt{H}, \texttt{HR}, \texttt{R}, \texttt{RA}, \texttt{W}, and \texttt{L}. Only keep seasons dating back to 1990, and remove the 1994, 1995, and 2020 seasons. 
  
```{r question1}
newTeams <- Teams %>%
  select(yearID, teamID, AB, SO, H, HR, R, RA, W, L) %>%
  filter(yearID >= "1990") %>%
  filter(yearID != "1994") %>%
  filter(yearID != "1995") %>%
  filter(yearID != "2020")

#852

#question 1b
bwar_bat = readr::read_csv("https://www.baseball-reference.com/data/war_daily_bat.txt", na = "NULL")
bwar_pit = readr::read_csv("https://www.baseball-reference.com/data/war_daily_pitch.txt", na = "NULL")  

bwar_bat <- bwar_bat %>%
  filter(year_ID >= "1990") %>%
  filter(year_ID != "1994") %>%
  filter(year_ID != "1995") %>%
  filter(year_ID != "2020") %>%
  filter(year_ID != "2022")

bwar_pit <- bwar_pit %>%
  filter(year_ID >= "1990") %>%
  filter(year_ID != "1994") %>%
  filter(year_ID != "1995") %>%
  filter(year_ID != "2020") %>%
  filter(year_ID != "2022")

WARdef_pull <- bwar_bat %>%
  select(name_common, team_ID, year_ID, WAR_def)
#40291

#need to groupby(team_ID, year_ID)
BRruns_pull <- bwar_bat %>%
  select(name_common, team_ID, year_ID, runs_br)
#40291
bullpen_war_pull <- bwar_pit %>%
  select(team_ID, year_ID, IPouts,
         IPouts_relief, WAR) %>%
  filter((IPouts_relief/ IPouts) >= 0.75)
#12298

teamdWAR <- WARdef_pull %>%
  group_by(year_ID, team_ID) %>%
  na.omit(WAR_def) %>%
  summarise(dWAR = sum(WAR_def))
  
teamBRruns <- BRruns_pull %>%
  group_by(year_ID, team_ID)  %>%
  summarise(BRruns = sum(runs_br))

teamPenWAR <- bullpen_war_pull %>%
  group_by(year_ID, team_ID) %>%
  summarise(penWAR = sum(WAR))

teamPenWAR$penWAR <- round(teamPenWAR$penWAR ,digits = 2)
teamBRruns$BRruns <- round(teamBRruns$BRruns ,digits = 2)
teamdWAR$dWAR <- round(teamdWAR$dWAR ,digits = 2)
#need to figure out all the rounding stuff

#question 1c 

newTeams$teamID <- str_replace(newTeams$teamID, "CHA", "CHW")
newTeams[newTeams == "CHN"] <- "CHC"
newTeams[newTeams == "KCA"] <- "KCR"
newTeams[newTeams == "LAN"] <- "LAD"
newTeams[newTeams == "ML4"] <- "MIL"
newTeams[newTeams == "NYA"] <- "NYY"
newTeams[newTeams == "NYN"] <- "NYM"
newTeams[newTeams == "SDN"] <- "SDP"
newTeams[newTeams == "SFN"] <- "SFG"
newTeams[newTeams == "TBA"] <- "TBR"
newTeams[newTeams == "WAS"] <- "WSN"
newTeams[newTeams == "FLO"] <- "FLA"
newTeams$teamID <- str_replace(newTeams$teamID, "SLA", "STL")

teams <- newTeams %>%
  group_by(yearID, teamID)

newTeams <- cbind(teams, teamdWAR$dWAR, teamBRruns$BRruns, teamPenWAR$penWAR)

colnames(newTeams)[colnames(newTeams) == "...11"] ="dWAR"
colnames(newTeams)[colnames(newTeams) == "...12"] ="BRruns"
colnames(newTeams)[colnames(newTeams) == "...13"] ="penWAR"


#question 1d
newTeams <- newTeams %>%
  mutate(RD = R - RA)

#Compute and add winning percentage \texttt{Wpct} to your data frame. Use an equation in your notes and linear regression to compute the optimal $k$ so that \texttt{Wpct} is well-explained by \texttt{Wpytk} = $R^k/(R^k + RA^k)$. Add \texttt{Wpytk} and \texttt{residuals\_pytk = Wpct - Wpytk} to your data frame. 

#question 1e

q1e <- newTeams %>%
  mutate(Wpct = W / (W + L))

dat_aug <- newTeams %>% 
  mutate(logWratio = log(W / L), 
         logRratio = log(R / RA))

pyFit <- lm(logWratio ~ 0 + logRratio, data = dat_aug)
pyFit


#Display the rows of this data frame corresponding to the 2014-2015 Royals seasons.

royals <- dat_aug %>%
  filter(yearID == "2014" | yearID == "2015") %>%
  filter(teamID == "KCR")

```

**Question 2** In this problem we will perform analyses that investigate strengths and peculiarities of the 2014-2015 Royals. Do the following:

  - Fit and analyze a regression model of \texttt{residuals\_pytk} on \texttt{penWAR}. Determine how many wins one would expect the Royals to obtain above their Pythagorean expectations on the basis of their bullpen.
  
```{r question2}

dat_aug <- dat_aug %>% 
  mutate(Wpct = W / (W + L)) %>%
  mutate(Wpct_pyt = R^2 / (R^2 + RA^2)) %>%
  mutate(residuals_pytk = Wpct - Wpct_pyt)

m3 <- lm(penWAR ~ 0 + Wpct_pyt, data = dat_aug)
m3




0.02991 *162

#The Royals' bullpen WAR outpaced their Pythagorean wins by 4.85 wins, on average.

```

  

**Question 3** Do the following: 

  - Select a period of your choice (at least 20 years) and fit the Pythagorean formula model (after finding the optimal exponent) to the run-differential, win-loss data.
  
```{r question3a}
q3a <- dat_aug %>%
  filter (yearID >= "2000") %>%
  mutate(logWLratio = log(W/L),
         logRDratio = log(R/RA))

fitted <- lm(logWLratio ~ 0 + logRDratio, data = q3a)
fitted

q3a <- q3a %>%
  mutate(W_pyt = (W ^ 1.845 / (W ^ 1.845 + L ^ 1.845)) *162 )  %>%
  mutate(RD_pyt = (R ^ 1.845 / (R ^ 1.845 + RA ^ 1.845)) *162 ) %>%
  mutate(RD_resid = RD - RD_pyt) %>%
  mutate(W_resid = W - W_pyt)
```  
  
  - On the basis of your fit in the previous part and the list of managers obtained from Retrosheet, compile a top 10 list of managers who most overperformed their Pythagorean winning percentage and a top 10 list of managers who most underperformed their Pythagorean winning percentage.

```{r underperformingmanagers}

#underperforming managers
underperform <- q3a[order(q3a$W_resid), ]
head(underperform, 10)
```
Managers:
2001 Seattle: pinielo01 & mclarjo99
2018 Boston: coraal01
2019 Houston: hinchaj01
2021 San Francisco: kaplega01
2019 Los Angeles Dodgers: roberda07
2021 Los Angeles Dodgers: roberda07
2004 St. Louis: larusto01
2002 New York Yankees: torrejo01
2016 Chicago Cubs: maddojo99
2002 Atlanta: coxbo01
```{r overperformingmanagers}
#overperforming managers

overperform <- q3a[order(-q3a$W_resid), ]
head(overperform, 10)
```
Managers: 
2003 Detroit: trammal01
2018 Baltimore: showabu99
2019 Detroit: gardero01
2004 Arizona: brenlbo01 & pedrial01
2013 Houston: portebo03
2021 Arizona: lovulto01
2021 Baltimore: hydebr99
2019 Baltimore: hydebr99
2012 Houston: millsbr01 & defrato99
2002 Milwaukee: lopesda01 & roystje01
**Question 4** The first question on page 21 in Section 1.4.3 of Analyzing Baseball Data with R.   
  
 - During the McGwire/Sosa home run race, which player was more successful at hitting homers with men on base?
 
Mark McGwire hit 37 home runs in 313 plate appearances with runners on base, while Sammy Sosa hit 29 in 367. Once walks (both intentional and unintentional) and hit by pitches are removed, the number of opportunities become 223 for McGwire and 317 for Sosa.

```{r question4a}
#fields <- Batting %>%
#fields <- read.csv("fields.csv")

#I am very stressed and confused
#I think we'll end up needing year-by-year data, similar to the dataset we worked on in class

```

